---
title: "Logit model for Project3"
author: "Edwige"
date: "October 25, 2015"
output: html_document
---

```{r}
library(tidyr)
library(dplyr)
library(RCurl)
library(aod)
library(reshape2)

all_df<- read.csv('project_view_year_numeric_CLEANED.csv', stringsAsFactors=FALSE)

#We will use a subset of the dataset with categories "FILM EDITING", "CINEMATOGRAPHY", "DIRECTING" and "BEST PICTURE".
part_df2<- subset(all_df, Category %in% c("FILM EDITING", "BEST PICTURE", "CINEMATOGRAPHY", "DIRECTING"))

#Using dcast function from the reshape2 library to transform the variables "Won" and categories "CINEMATOGRAPHY", "DIRECTING", "BEST PICTURE" and "FILM EDITING" into variables "BEST PICTURE_no", "BEST PICTURE_yes", "FILM EDITING_no" and "FILM EDITING_yes", DIRECTING_YES, DIRECTING_NO, CINEMATOGRAPHY_YES, CINEMATOGRAPHY_NO

dichot2<-dcast(part_df2, Year+Nominee ~ Category+Won)
head(dichot2)
dtframe<- dichot2

#Changing the variable names 
thecolnames<-c("Year", "Nominee","BestPic_NO", "BestPic_YES", "Cinemato_NO", "Cinemato_YES", "Directing_NO", "Directing_YES", "FilmEdit_NO", "FilmEdit_YES")
names(dtframe)<-thecolnames

head(dtframe)
dtframe<-as.data.frame(dtframe)

# Taking care of Missing Values
# 1- Creating two columns on nomination status: Nominee_BP and Nominee_FE. If the values of BestPic_NO and BestPic_YES are not available, Nominee_BP is NO, otherwise, Nominee_BP is YES.

#If the values of FilmEdit_NO and FilmEdit_YES are not available, Nominee_FE is NO, otherwise, Nominee_FE is YES.

for (i in 1:nrow(dtframe))
{ 
ifelse (((is.na(dtframe[i,"BestPic_NO"])) && (is.na(dtframe[i,"BestPic_YES"]))), dtframe[i,"Nominee_BP"]<-"NO", dtframe[i,"Nominee_BP"]<-"YES")
  
ifelse (((is.na(dtframe[i,"Cinemato_NO"])) && (is.na(dtframe[i,"Cinemato_YES"]))), dtframe[i,"Nominee_CI"]<-"NO", dtframe[i,"Nominee_CI"]<-"YES")

ifelse (((is.na(dtframe[i,"Directing_NO"])) && (is.na(dtframe[i,"Directing_YES"]))), dtframe[i,"Nominee_DI"]<-"NO", dtframe[i,"Nominee_DI"]<-"YES")

ifelse (((is.na(dtframe[i,"FilmEdit_NO"])) && (is.na(dtframe[i,"FilmEdit_YES"]))),  dtframe[i,"Nominee_FE"]<-"NO", dtframe[i,"Nominee_FE"]<-"YES")
}

dtframe2<-dtframe
# Taking care of Missing Values
# 2- Transforming missing values to NO
for (i in 1:nrow(dtframe2))
{ 
if (is.na(dtframe2[i,"BestPic_NO"])) dtframe2[i,"BestPic_NO"]<-"NO"
if (is.na(dtframe2[i,"BestPic_YES"])) dtframe2[i,"BestPic_YES"]<-"NO"
if (is.na(dtframe2[i,"Cinemato_NO"])) dtframe2[i,"Cinemato_NO"]<-"NO"
if (is.na(dtframe2[i,"Cinemato_YES"])) dtframe2[i,"Cinemato_YES"]<-"NO"
if (is.na(dtframe2[i,"Directing_NO"])) dtframe2[i,"Directing_NO"]<-"NO"
if (is.na(dtframe2[i,"Directing_YES"])) dtframe2[i,"Directing_YES"]<-"NO"
if (is.na(dtframe2[i,"FilmEdit_NO"])) dtframe2[i,"FilmEdit_NO"]<-"NO"
if (is.na(dtframe2[i,"FilmEdit_YES"])) dtframe2[i,"FilmEdit_YES"] <-"NO"
}
head(dtframe2)

#some fields are in upper case, the other in lower case. We are going to change everything to upper case
dtframe2$BestPic_NO <- toupper(dtframe2$BestPic_NO)
dtframe2$BestPic_YES <- toupper(dtframe2$BestPic_YES)
dtframe2$FilmEdit_NO <- toupper(dtframe2$FilmEdit_NO)
dtframe2$FilmEdit_YES <- toupper(dtframe2$FilmEdit_YES)
dtframe2$Cinemato_NO <- toupper(dtframe2$Cinemato_NO)
dtframe2$Cinemato_YES <- toupper(dtframe2$Cinemato_YES)
dtframe2$Directing_NO <- toupper(dtframe2$Directing_NO)
dtframe2$Directing_YES <- toupper(dtframe2$Directing_YES)
dtframe2$Nominee_BP <- toupper(dtframe2$Nominee_BP)
dtframe2$Nominee_BP <- toupper(dtframe2$Nominee_BP)
dtframe2$Nominee_CI <- toupper(dtframe2$Nominee_CI)
dtframe2$Nominee_DI <- toupper(dtframe2$Nominee_DI)

str(dtframe2)


#For our modelisation, we will keep two variables:"BestPic_YES"and "FilmEdit_YES",  from "BestPic_NO", "BestPic_YES", "FilmEdit_NO", "FilmEdit_YES". We will rename those variables to Won_BP (won BEST PICTURE) and Won_FE (won "FILM EDITING")

dtframe2$Won_BP<-dtframe2$BestPic_YES
dtframe2$Won_CI<-dtframe2$Cinemato_YES
dtframe2$Won_DI<-dtframe2$Directing_YES
dtframe2$Won_FE<-dtframe2$FilmEdit_YES
dtframe2$FilmEdit_YES<-NULL
dtframe2$BestPic_YES<-NULL
dtframe2$BestPic_NO<-NULL
dtframe2$FilmEdit_NO<-NULL
dtframe2$Cinemato_YES<-NULL
dtframe2$Directing_YES<-NULL
dtframe2$Cinemato_NO<-NULL
dtframe2$Directing_NO<-NULL
#estimates a logistic regression model using the glm (generalized linear model) function
#Changing character columns into factors 

dtframe2$Won_FE <- as.factor(dtframe2$Won_FE)
dtframe2$Won_BP <- as.factor(dtframe2$Won_BP)
dtframe2$Nominee_BP <- as.factor(dtframe2$Nominee_BP)
dtframe2$Nominee_FE <- as.factor(dtframe2$Nominee_FE)
dtframe2$Won_DI <- as.factor(dtframe2$Won_DI)
dtframe2$Won_CI <- as.factor(dtframe2$Won_CI)
dtframe2$Nominee_CI <- as.factor(dtframe2$Nominee_CI)
dtframe2$Nominee_DI <- as.factor(dtframe2$Nominee_DI)
#Building the model
#Won_BP and Nominee_BP are correlated, we add Nominee_BP in our model, but we are not expecting any findings from that variable.
model2<-glm(Won_BP~Won_FE+Nominee_FE+Won_DI+Won_CI+Nominee_CI+Nominee_DI, data=dtframe2,family="binomial")


#Using the command summary to get the results
summary(model2)

```



In the output from the summary command, the first thing we see is the call, a reminder about what the model we ran was, what options we specified, etc.

Next we see the deviance residuals, which are a measure of model fit. This part of output shows the distribution of the deviance residuals for individual cases used in the model. 

The next part of the output shows the coefficients, their standard errors, the z-statistic (Wald z-statistic), and the associated p-values. 

`Won_DI`, `Nominee_DI`, `Won_FE` and `Nominee_FE` are statistically significant at the:

1- 5% level for `Won_FE`, p-value 0.01720, 

2- 1% level for `Nominee_DI` and `Nominee_FE`, p-values 0.00381 and 0.00370 

3- 0% level for `Won_DI`, p-value < 2e-16. 

The data we have seems to indicate that "FILM EDITING' and "DIRECTING" are influential in predicting "BEST PICTURE". 


```{r}

## Confidence Intervals using standard errors
confint.default(model2)


## odds ratios only
exp(coef(model2))
```
