---
title: "Project_3_t-test"
author: "Diego Diaz"
date: "October 22, 2015"
output: 
  html_document: 
    highlight: tango
    theme: readable
    toc: yes
---

#Objective

#Required Libraries
```{r libraries}

library(tidyr)
library(dplyr)
library(RCurl)


```

#Loading the Data

```{r loading_data}

url <- getURL("https://raw.githubusercontent.com/mkds/IS607_Project3/gh-pages/Data/project_view_year_numeric_CLEANED.csv")

mydata <- read.csv(text = url) 


head(mydata)
str(mydata)


```

#Data Transformation

```{r transformation}

mydata2 <- mutate(mydata, TEST = ifelse(Won == "yes", 1, 0))

head(mydata2)

```



#Subsetting

```{r subsetting}

#Rest
rt <- filter(mydata2, Category != "FILM EDITING" & Category != "BEST PICTURE")

#Film Editing
ed <- filter(mydata2, Category == "FILM EDITING")

#Best Picture
bp <- filter(mydata2, Category == "BEST PICTURE")

#Cinematography
cm <- filter(mydata2, Category == "CINEMATOGRAPHY")

#Directing
dr <- filter(mydata2, Category == "DIRECTING")


#Special Effects
sp <- filter(mydata2, Category == "SPECIAL EFFECTS")


#Sound Editing
sm <- filter(mydata2, Category == "SOUND MIXING")


#Actor in leading role
ar <- filter(mydata2, Category == "ACTOR IN A LEADING ROLE")


```

#Left Joins


> Rest vs. Best Picture

```{r joins_rest_bp}

#Left join for Rest vs. Best Picture
lj1 <- left_join(rt,bp, by = "Nominee")

#Selecting the TEST column
lj1 <- unlist(select(lj1,TEST.y))

#Converting NAs to zeros
lj1[is.na(lj1)] <- 0 


```



> Film Editing vs. Best Picture

```{r joins_editing_bp}
#Left join for Film Editing vs. Best Picture
lj2 <- left_join(ed,bp, by = "Nominee")


#Selecting the TEST column
lj2 <- unlist(select(lj2,TEST.y))


#Converting NAs to zeros
lj2[is.na(lj2)] <- 0


```

> Cinematography vs. Best Picture 

```{r joins_editing_cinematography}
#Left join for Cinematography vs. Best Picture
lj3 <- left_join(cm,bp, by = "Nominee")

#Selecting the TEST column
lj3 <- unlist(select(lj3,TEST.y))

#Converting NAs to zeros
lj3[is.na(lj3)] <- 0 

```

> Directing vs. Best Picture

```{r joins_editing_directing}
#Left join for Directing vs. Best Picture
lj4 <- left_join(dr,bp, by = "Nominee")

#Selecting the TEST column
lj4 <- unlist(select(lj4,TEST.y))

#Converting NAs to zeros
lj4[is.na(lj4)] <- 0 

```


> Special Effects vs. Best Picture

```{r joins_editing_effects}
#Left join for Special Effects vs. Best Picture
lj5 <- left_join(sp,bp, by = "Nominee")

#Selecting the TEST column
lj5 <- unlist(select(lj5,TEST.y))

#Converting NAs to zeros
lj5[is.na(lj5)] <- 0 

lj5 <- unlist(lj5)

```

> Sound Mixing vs. Best Picture

```{r joins_editing_sound}
#Left join for Sound Sound Mixing vs. Best Picture
lj6 <- left_join(sm,bp, by = "Nominee")

#Selecting the TEST column
lj6 <- unlist(select(lj6,TEST.y))

#Converting NAs to zeros
lj6[is.na(lj6)] <- 0

```

> Actor in Leading Role vs. Best Picture

```{r joins_editing_actor}
#Left join for Actor in Laeding Role vs. Best Picture
lj7 <- left_join(ar,bp, by = "Nominee")

#Selecting the TEST column
lj7 <- unlist(select(lj7,TEST.y))

#Converting NAs to zeros
lj7[is.na(lj7)] <- 0 

```



#F and T-Test Analysis


> Film Editing  vs. Rest

**F-Test**

```{r bp_rest_f}

var.test(lj2,lj1)


```

**T-Test**
```{r bp_rest_t}

t.test(lj2,lj1, var.equal=FALSE, paired=FALSE)

```


> Film Editing vs. Cinematography 

**F-Test**

```{r bp_cinematography_f}

var.test(lj2,lj3)


```

**T-Test**
```{r bp_cinematography_t}

t.test(lj2,lj3, var.equal=TRUE, paired=FALSE)

```


> Film Editing vs. Directing


**F-Test**

```{r bp_directing_f}

var.test(lj2,lj4)


```

**T-Test**
```{r bp_directing_t}

t.test(lj2,lj4, var.equal=TRUE, paired=FALSE)

```

> Fild Editing vs. Special Effects

```{r bp_effects_f}

#var.test(lj2,lj5)


```

**T-Test**
```{r bp_effects_t}

#t.test(lj2,lj5, var.equal=FALSE, paired=FALSE)

```
> Film Editing vs. Sound Mixing

```{r bp_mixing_f}

var.test(lj2,lj6)

  
```

**T-Test**
```{r bp_mixing_t}

t.test(lj2,lj6, var.equal=TRUE, paired=FALSE)

```

> Film Editing vs. Actor in Leading Role


```{r bp_actor_f}

var.test(lj2,lj7)


```

**T-Test**
```{r bp_actor_t}

t.test(lj2,lj7, var.equal=FALSE, paired=FALSE)

```

#Conclusion

